Legends for supplementary material

### 2019-03-11 Manuscript/Figures/figure_legends.Rmd
added to figure legends

>>>>

**Figure 6. Variable importance of the top 20 most predictive genomic annotations for models using SMOTE resampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using SMOTE resampling, for each cell line respectively.

### 2019-03-11 Manuscript/Supplementary/supplementary_legends.Rmd
added to figure legends

>>>>

**Figure 6. Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model with distance-type predictors at the 10 kb data resolution, while not performing a class balancing technique, for each cell line respectively.

**Figure 7. Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random over-sampling to create balanced classes, for each cell line respectively.

**Figure 8. Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random under-sampling to create balanced classes, for each cell line respectively.
